\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-28 paper.tex
Update Figure 6
removing eval falsse

XXX Prediction should have a jitter option, to spread the predicted
points out fully in the hexagons.

@@

\includegraphics{figures/mnist/mnist_model_2d.png}

@@

\includegraphics{figures/mnist/img_error_sample_within.png}

@@

\includegraphics{figures/mnist/img_error_sample_out.png}

>>>>

@@

\captionsetup{labelsep=none}\includegraphics{figures/mnist/mnist_model_2d.png}

@@

\captionsetup{labelsep=none}\includegraphics{figures/mnist/img_error_sample_within.png}

@@

\captionsetup{labelsep=none}\includegraphics{figures/mnist/img_error_sample_out.png}
